% With the development of deep learning, model-based Single Image Super Resolution(SISR) have achieved tremendous successes recently and outperformed traditional methods in many synthetic datasets. Nonetheless, when applying these methods to real low resolution images, the SR effect is significantly lower than that of synthetic images, and unexpected artifacts will occur at the same time. The main reason is that synthetic datasets often assume that the images are degrated in a deterministic manner, such as gaussian blur and bicubic downsampling, while real low resolution images usually have unknown degradation processes including unknown noise, blur, image compression, etc., thus affecting the performance of SR effects of the trained models.

% To alleviate this problem, the model can be trained by real paired datasets, such as City100, RealSR, etc. However, it is laborious and expensive to collect real paired images and models trained in this way may not be applied to other datasets for the domain distance between different datasets. In recent years, many unsupervised learning based models have been proposed, that is, training a downsampling network using unpaired datasets considering the degradation process, and generating enormous number of pseudo-paired images with it. The super resolution model can be trained by the generated datasets supervisedly to cut data collection custs and improve the generalization of the model.

% Recently, Ning et al. proposed USR-DU that models the uncertainty of the image degradation process, which outperforms the state of the art models in many datasets. The model has excellent performance on images with low blur, while performs poorly on those with high blur. To solve this problem, we proposed an improved model \textbf{UBSR-DU}. Firstly, we compared the generated low resolution images and the real ones.

Single Image Super-Resolution (SISR) technology aims to improve the clarity and detail of images by increasing their resolution, making them more realistic. It has important applications in areas such as photography, surveillance, reconstruction of old images, etc. Real low-resolution (LR) images are often produced by complex and unknown degradation processes from their corresponding high-resolution (HR) images, making it laborious and costly to obtain paired training sets to train super-resolution models. In recent years, many unsupervised learning based models have been proposed, which train a downsampling network (DSN) using unpaired datasets, considering the image degredation process and a enormous number of pseudo-paired datasets are generated by such network. Train a super-resolution network (SRN) by using the generated datasets can alleviate the collection costs of paired datasets as well as improve the generalization of the model.

Recently, Ning et al. proposed USR-DU that models the uncertainty of the image degradation process, which outperforms the state of the art models in many datasets. Despite the excellent results, the model performs poorly on those with high blur. To solve this problem, we proposed an improved model \textbf{UBSR-DU}. Firstly, we analyzed the design of the downsampling network part of USR-DU and found its drawback comes from the ignorance of blur in degradation process during the DSN part. To integrate the blur information into the DSN, we analyzed different kernel estimation methods and eventually adopted MANet, which estimates spatially-variant blur kernels. Thereafter, we designed a training procedure that firstly estimates the blur kernels of the LR image patches in the training batch and then apply them into the generation procedure of reference images of DSN, thus successfully fused blur information into the DSN. Furthermore, considering that there are more texts in the test sets in this paper and fewer texts in the training sets, a few number of HR images containing texts are added into the training sets, which promote the reconstruction effect of texts in LR images in the test sets. Finally, by strict ablation study, we demonstrated the effectiveness and necessity of the improve proposals above. The proposed method is validated in the Canon 4x test sets of RealSR, and the experimental results show that it improves PSNR and SSIM by \textbf{0.07dB} and \textbf{0.0012} respectively, compared to the USR-DU model.